A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
Fixed bug with scaling.

\todo{rework this. It would be nice to compare Graphalytics and our approach on the real-world dataset.}
Table~\ref{tab:epg-perf}, by contrast, gives an overview of the performance results of running Graphalytics and our approach using the same dataset [TODO: Get the Dota-League Dataset working with easy-parallel-graph and replace Table~\ref{epg-perf}]. Table~\ref{tab:epg-perf} shows the average time across 32 roots, whereas Graphalytics by default shows results for a single root.

@@

%\begin{table}
%	\centering
%	\begin{tabular}{l|c|c|c}
%		System & Load Graph & \begin{tabular}[x]{@{}c@{}}Construct Data \\ Structure\end{tabular} & Run BFS \\ \hline
%		Graph500 & 0.3474 & 0.3971 & 0.003380 \\
%		GAP      & 2.351  & 0.1935 & 0.001393 \\
%		GraphMat & 0.1511 & 1.101  & 0.1031 \\
%		GraphBIG & 37.22  & N/A    & 0.1528 \\
%	\end{tabular}
%	\caption{This table shows times for $2^{20}$ verties and the times are in seconds. The Graph500 generates the graph instead of loading it into a file. GraphBIG builds the graph and reads in the file simultaneously. These results were averaged across 32 roots.}
%	\label{tab:epg-perf}
%\end{table}

@@

Figure~\ref{fig:bfs-scaling} shows the scalability and speedup for BFS. We define the strong scaling as $T_1 / (n T_n)$ where $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ is the time for $n$ threads. A linear scalability is when $T_n = T_1/n$ and is the horizontal line on the bottom plot in Fig.~\ref{fig:bfs-scaling}. These plots show in general poor scaling throughout, although GraphBIG has the best scaling. A potential explanation is GraphBIG is the slowest system, so there is more room for improvement. Additionally, $2^{20}$ vertices is a ``small'' graph by today's standards and thus library designers focus on scalability for larger graphs. Another limitation may be the ability for OpenMP to efficiently handle such a large number of threads per machine.
\begin{figure}
	\centering
	\begin{minipage}{0.9\linewidth}
		% trim=left lower right upper
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_speedup.pdf}
	\end{minipage}
	\begin{minipage}{0.9\linewidth}
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_ss.pdf}
	\end{minipage}
	\caption{The top figure has both axes logarithmic with an exception at 72 threads for readability. Linear speedup is. GraphMat dips below 1 because it is slower for $2$ threads than for 1. $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ time for $n$ threads.}
	\label{fig:bfs-scaling}
\end{figure}
\todo{Rerun GraphMat on scale 22 with 2 threads. Surprising that it slows down}

@@

Overall, the GAP Benchmark Suite was the highest-performing system across the given datasets but the least scalable. However, this is only for relatively small graphs; all the graphs used here had at most $2^{22}$ vertices. It should be noted that GAP is also the most recent of projects. Thus, we recommend graph processing algorithm designers compare their implementations against the GAP Benchmark Suite as a good test of performance.

We found that GraphMat is not highly performant but does scale relatively well. One explanation is that GraphMat's underlying computation model (sparse matrix operations), paired the increased overhead of GraphMat's doubly-compressed sparse row (DSCR) graph representation, is better suited to larger-scale graphs.
% Furthermore, sparse matrix operations have been well studied so achieving good scalability is more realistic [cite]

>>>>

% Table~\ref{tab:epg-perf}, by contrast, gives an overview of the performance results of running Graphalytics and our approach using the same dataset [TODO: Get the Dota-League Dataset working with easy-parallel-graph and replace Table~\ref{epg-perf}]. Table~\ref{tab:epg-perf} shows the average time across 32 roots, whereas Graphalytics by default shows results for a single root.
%\begin{table}
%	\centering
%	\begin{tabular}{l|c|c|c}
%		System & \begin{tabular}[x]{@{}c@{}}Construct Data \\ Structure\end{tabular} & Run BFS & Run SSSP \\ \hline
%		PowerGraph & N/A & 0.003380 \\
%		GAP        & 0.412 & 0.001393 \\
%		GraphMat   &  & 0.1031 \\
%		GraphBIG   & N/A & 0.1528 \\
%	\end{tabular}
%	\caption{This table shows times for the Dota-League dataset using our method.}
%	\label{tab:epg-perf}
%\end{table}

@@

@@

Figure~\ref{fig:bfs-scaling} shows the scalability and speedup for BFS. We define the strong scaling as $T_1 / (n T_n)$ where $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ is the time for $n$ threads. A linear scalability is when $T_n = T_1/n$ and is the horizontal line on the bottom plot in Fig.~\ref{fig:bfs-scaling}. These plots show in general poor scaling throughout, although GraphBIG has the best scaling. A potential explanation is that because GraphBIG is the slowest system, there is more room for improvement. Additionally, $2^{20}$ vertices is a ``small'' graph by today's standards and thus library designers focus on scalability for larger graphs. Another limitation may be the ability for OpenMP to efficiently handle such a large number of threads per machine.
\begin{figure}
	\centering
	\begin{minipage}{0.9\linewidth}
		% trim=left lower right upper
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_speedup.pdf}
	\end{minipage}
	\begin{minipage}{0.9\linewidth}
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_ss.pdf}
	\end{minipage}
	\caption{The top figure has both axes logarithmic with an exception at 72 threads for readability. Linear speedup is. GraphBIG dips below 1 because it is slower for $2$ threads than for 1. $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ time for $n$ threads.}
	\label{fig:bfs-scaling}
\end{figure}
\todo{Rerun GraphMat on scale 22 with 2 threads. Surprising that it slows down}

@@

Overall, the GAP Benchmark Suite was the highest-performing system across the given datasets though not the most scalable. However, this is only for relatively small graphs; all the graphs used here had at most $2^{22}$ vertices. It should be noted that GAP is also the most recent of projects. Thus, we recommend graph processing algorithm designers compare their BFS implementations to the Graph500 for BFS, GAP Benchmark Suite for smaller problem sizes or a low number of cores (at most 32), and GraphMat for larger problems with more cores.

We found that GraphMat is relatively performant and scales better at higher cores. One explanation is that GraphMat's underlying computation model (sparse matrix operations), paired with the increased overhead of GraphMat's doubly-compressed sparse row (DSCR) graph representation, is better suited to larger-scale graphs.
% Furthermore, sparse matrix operations have been well studied so achieving good scalability is more realistic [cite]
